### 2019-03-24 Introduction.tex
Updates from Overleaf

\section{Mapping Sequences to Sets} 
\kechen{officialy define T, N, $x^{(n)}$} In this section, we formulate how existing works map sequences to sets, by writing down their objective functions using consistent notations. To review RNN designed for sequences, let $\mathbf{s}=(s_1,s_2,...,s_T)$ be an input sequence of outcomes, in a particular order; the order is often critical to the datapoint. An RNN model defines a probability distribution over all possible output sequences given the input in the form $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)=\prod_{t=1}^T p(s_t|x,s_1,s_2,...,s_{t-1})$. To train the RNN model, one maximizes the likelihood of the ground truth sequence $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)$.

@@

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g.\ by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})\\
\label{eq:standard_rnn}
\end{align}
\newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:

>>>>

\section{Mapping Sequences to Sets} 
In this section, we formulate how existing works map sequences to sets, by writing down their objective functions using consistent notations. To review RNN designed for sequences, let $\mathbf{s}=(s_1,s_2,...,s_T)$ be an input sequence of outcomes, in a particular order\kechen{, where $T$ is the maximum number of labels in a document}; the order is often critical to the datapoint. An RNN model defines a probability distribution over all possible output sequences given the input in the form $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)=\prod_{t=1}^T p(s_t|x,s_1,s_2,...,s_{t-1})$. To train the RNN model, one maximizes the likelihood of the ground truth sequence $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)$.

@@

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g.\ by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})
\label{eq:standard_rnn}
\end{align}
\kechen{where $N$ is the total number of samples in the corpus and $n$ represents the $n$-th sample.} \newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:
